14th International Satisfiability Modulo Theories Competition (SMT-COMP 2019): Rules and Procedures

### 2019-04-19 rules/rules19.tex
Rules: First pass over input/output.

\header{Wrapper Tool.}
%
A \emph{wrapper tool} is defined as any solver that calls one or more SMT
solvers (the \emph{wrapped solvers}) that do not have the same author as the
wrapper tool itself. Its system description \textbf{must} explicitly acknowledge any
solvers that it wraps.  It \emph{should} further make clear technical
innovations by which the wrapper tool expects to improve on the wrapped
solvers.

\header{Derived Tool.}
%
A \emph{derived tool} is defined as any solver that is \emph{based on and
extends} an SMT solver (the \emph{base solver}) not written by the authors of
the derived tool.  Its system description \textbf{must} explicitly acknowledge
the solver it is based on and extends.  It \emph{should} further make clear
technical innovations by which the wrapper tool expects to improve on the
wrapped solvers.  A derived tool should follow the \emph{naming convention}
{[name of base solver]-[my solver name]}.

@@

\header{Input and output.}
%
In the \maintrack, \mvaltrack, \ucoretrack and \challtrack, a participating
solver must read a single benchmark script, whose filename is presented as the
solver's first command-line argument.  In the \inctrack, a trace
executor will send commands from a benchmark script to the solver's standard
input channel.

The benchmark script is in the concrete syntax of the SMT-LIB format,
version~2.6, though with a restricted set of commands.  A benchmark
script is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
\item
  \begin{enumerate}
  \item In the \maintrack and \ucoretrack, there may be a single
    \akey{(set-option :print-success ...)} command.  Note that
    \texttt{success} outputs are ignored by the post-processor used by
    the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
      a \texttt{success} answer after each \akey{set-logic},
      \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
      command (among others), unless the option \akey{:print-success}
      is set to false.  Ignoring the \texttt{success} outputs allows
      for submitting fully SMT-LIB~2.6 compliant solvers without the
      need for a wrapper script, while still allowing entrants of
      previous competitions to run without changes.}
  \item In the incremental track, the \akey{:print-success} option
    must not be disabled.  The trace executor will send an initial
      \akey{(set-option :print-success true)} command to the solver.
  \end{enumerate}
\item In the \ucoretrack, there is a single \akey{(set-option
  :produce-unsat-cores true)} command.
\item The (single) \akey{set-logic} command setting the benchmark's
  logic is the first command after any \akey{set-option} commands.
\item The script may contain any number of \akey{set-info} commands.
\item The script may contain any number of \akey{declare-sort} and
  \akey{define-sort} commands.  All sorts declared or defined with
  these commands must have zero arity.
\item The script may contain any number of \akey{declare-fun} and
  \akey{define-fun} commands.
\item If the benchmark's logic features algebraic datatypes, the
  script may contain any number of \akey{declare-datatype(s)}
  commands.
\item The script may contain any number of \akey{assert} commands.
  All formulas in the script belong to the benchmark's logic, with any
  free symbols declared in the script.
\item
  \begin{enumerate}
    \item In all tracks except the \ucoretrack,  named terms (i.e., terms
      with the \akey{:named} attribute) are not used.
    \item In the \ucoretrack, top-level assertions may be named.
  \end{enumerate}
\item
  \begin{enumerate}
  \item In all tracks except the \inctrack, there is exactly one
    \akey{check-sat} command.
  \item In the incremental track, there are one or more
    \akey{check-sat} commands.  There may also be zero or more
    \akey{push 1} commands, and zero or more \akey{pop 1} commands,
    consistent with the use of those commands in the SMT-LIB standard.
  \end{enumerate}
\item In the \ucoretrack, the \akey{check-sat} command (which is
  always issued in an unsatisfiable context) is followed by a single
  \akey{get-unsat-core} command.
\item In the \mvaltrack, the \akey{check-sat} command (which is
  always issued in a satisfiable context) is followed by a single
  \akey{get-model} command.
\item The script may optionally contain an \akey{exit} command as its
  last command.  In the incremental track, this command must not be
  omitted.
\item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.

>>>>

\header{Wrapper Tool.}
%
A \emph{wrapper tool} is defined as any solver that calls one or more other SMT
solvers (the \emph{wrapped solvers}). Its system description \textbf{must} explicitly acknowledge any
solvers that it wraps.  It \emph{should} further make clear technical
innovations by which the wrapper tool expects to improve on the wrapped
solvers.

\header{Derived Tool.}
%
A \emph{derived tool} is defined as any solver that is \emph{based on and
extends} another SMT solver (the \emph{base solver}).  Its system description
\textbf{must} explicitly acknowledge
the solver it is based on and extends.  It \emph{should} further make clear
technical innovations by which the derived tool expects to improve on the
original solver.  A derived tool should follow the \emph{naming convention}
{[name of base solver]-[my solver name]}.

@@

\header{Input and output.}
%
In the \emph{\inctrack}, the \emph{trace executor} will send commands from an
(incremental) benchmark file to the standard input channel of the solver.  In
\emph{all other tracks}, a participating solver must read a \emph{single}
benchmark file, whose filename is presented as the first command-line argument
of the solver.

Benchmark files are in the concrete syntax of the SMT-LIB format
version~2.6, though with a \emph{restricted} set of commands.  A benchmark
file is a text file containing a sequence of SMT-LIB commands that
satisfies the following requirements:
%
\begin{enumerate}
  \item
    \begin{enumerate}
      \item In the \textbf{\maintrack} and \textbf{\ucoretrack}, there may be a single
      \akey{(set-option :print-success ...)} command.  Note that
      \texttt{success} outputs are ignored by the post-processor used by
      the competition.\footnote{SMT-LIB~2.6 requires solvers to produce
        a \texttt{success} answer after each \akey{set-logic},
        \akey{declare-sort}, \akey{declare-fun} and \akey{assert}
        command (among others), unless the option \akey{:print-success}
        is set to false.  Ignoring the \texttt{success} outputs allows
        for submitting fully SMT-LIB~2.6 compliant solvers without the
        need for a wrapper script, while still allowing entrants of
        previous competitions to run without changes.}
      \item In the \textbf{\inctrack}, the \akey{:print-success} option
      must not be disabled.  The trace executor will send an initial
        \akey{(set-option :print-success true)} command to the solver.
      \item In the \textbf{\ucoretrack}, there is a single \akey{(set-option
        :produce-unsat-cores true)} command.
    \end{enumerate}
  \item A (single) \akey{set-logic} command is the \emph{first} command after
    any \akey{set-option} commands.
  \item It may contain any number of \akey{set-info} commands.
  \item It may contain any number of \akey{declare-sort} and
    \akey{define-sort} commands.  All sorts declared or defined with
    these commands must have zero arity.
  \item It may contain any number of \akey{declare-fun} and \akey{define-fun}
    commands.
  \item If the logic features algebraic datatypes, the benchmark file may
    contain any number of \akey{declare-datatype(s)} commands.
  \item It may contain any number of \akey{assert} commands.  All formulas in
    the file belong in the declared logic, with any free symbols declared in
    the file.
  \item
    \begin{enumerate}
      \item In \textbf{all} tracks \textbf{except} the \ucoretrack,  named
        terms (i.e., terms with the \akey{:named} attribute) are \emph{not}
        used.
      \item In the \textbf{\ucoretrack}, top-level assertions may be named.
    \end{enumerate}
  \item
    \begin{enumerate}
      \item In \textbf{all} tracks \textbf{except} the \inctrack, there is
        \emph{exactly one} \akey{check-sat} command.
      \item In the \textbf{\inctrack}, there are one or more
      \akey{check-sat} commands.  There may also be zero or more
      \akey{push 1} commands, and zero or more \akey{pop 1} commands,
      consistent with the use of those commands in the SMT-LIB standard.
    \end{enumerate}
  \item In the \textbf{\ucoretrack}, the \akey{check-sat} command (which is
    always issued in an unsatisfiable context) is followed by a single
    \akey{get-unsat-core} command.
  \item In the \textbf{\mvaltrack}, the \akey{check-sat} command (which is
    always issued in a satisfiable context) is followed by a single
    \akey{get-model} command.
  \item It may \emph{optionally} contain an \akey{exit} command as its
    last command.  In the \textbf{\inctrack}, this command must not be
    omitted.
  \item No other commands besides the ones just mentioned may be used.
\end{enumerate}
%
The SMT-LIB format specification is available from the ``Standard''
section of the SMT-LIB website~\cite{SMT-LIB}.  Solvers will be given
formulas only from the divisions into which they have been entered.
